---
title: "Readme"
author: "Me"
date: "10/19/2018"
output: md_document
---

```{r setup, include=FALSE}
library(prepr)
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation R

This package is used to temporarily relieve swelling, burning, pain, and itching caused by data preparation. Heavily influenced by sklearn preprocessing module. As such it aims to 
implement the Transformer API and allow for pipelines that can be saved and applied to 
new datasets.

It will eventually include methods for outputting to PMML or json to assist with productionalizing data preparation steps. It currently only works with single variables, but once the patterns are formalized it will extend to data.frames.

```{r}
# Dummy data
z1 <- rpois(1e5, 4)

## create a standard normalization scaler
scaler <- StandardScaler()

scaler$fit(z1)
hist(scaler$transform(z1))

## verify that the inverse transform is equal to the original data
all.equal(scaler$inverse_transform(scaler$transform(z1)), z1)

```

### Piplines

Pipelines simply chain together transformers in a list. They implement the Transformer
API as well and support the same methods:

```{r}
## chain together in a pipeline
p <- pipeline(
  StandardScaler(),
  MinMaxScaler(feature_range=c(-1, 1))
)

z2 <- p$fit_transform(z1)
z3 <- p$inverse_transform(z2)

## verify the pipeline can be undone
all.equal(z1, z3)
```



